Results

### 2019-03-13 analysis/02_analysis.Rmd
Use LaTeX in table headers since R&P doesn't use xelatex

tbl_likely_1 <- tbl_likely_tidy %>% 
  left_join(tbl_likely_probs, by = "title") %>% 
  filter(category == "Level 1") %>%
  mutate(title = recode(title, 
                        Crackdown = "Crackdown − No crackdown",
                        Issue = "*Humanitarian assistance − Human rights*",
                        Funding = "*Private − Government funding*")) %>% 
  mutate_at(vars(theta_1, theta_2, theta_diff, pct_change), 
            funs(percent_format(accuracy = 0.1)(.))) %>% 
  mutate(p.diff.not0 = as.character(round(p.diff.not0, 2))) %>%
  select(Frame = title, `% likely~Treatment~` = theta_2, `% likely~Control~` = theta_1,
         `∆` = theta_diff, `%∆` = pct_change, `p(∆ ≠ 0)` = p.diff.not0)
```

```{r tbl-likely-diffs-level2, warning=FALSE, message=FALSE}
tbl_likely_2 <- tbl_likely_tidy %>% 
  left_join(tbl_likely_probs, by = "title") %>% 
  filter(category == "Level 2") %>%
  mutate(title_clean = str_remove(title, " \\| Crackdown")) %>% 
  mutate(title_clean = case_when(
    title_clean %in% c("Human rights", "Humanitarian assistance") ~ paste(title_clean, "issues"),
    title_clean %in% c("Government", "Private") ~ paste(title_clean, "funding")
  )) %>% 
  mutate(title_clean = factor(title_clean, 
                              levels = c("Human rights issues", 
                                         "Humanitarian assistance issues", 
                                         "Government funding", "Private funding"))) %>% 
  arrange(title_clean) %>% 
  mutate_at(vars(theta_1, theta_2, theta_diff, pct_change), 
            funs(percent_format(accuracy = 0.1)(.))) %>% 
  mutate(p.diff.not0 = as.character(round(p.diff.not0, 2))) %>% 
  mutate(title_clean = as.character(title_clean)) %>% 
  select(`H~2a~ and H~3a~` = title_clean, 
         `% likely~Crackdown~` = theta_2, `% likely~No\\ crackdown~` = theta_1,
         `∆` = theta_diff, `%∆` = pct_change, `p(∆ ≠ 0)` = p.diff.not0)
```

```{r tbl-likely-diffs-level3, warning=FALSE, message=FALSE}
tbl_likely_3 <- tbl_likely_tidy %>% 
  left_join(tbl_likely_probs, by = "title") %>% 
  filter(category == "Level 3") %>%
  mutate(title_clean = str_remove(title, " \\| Crackdown")) %>% 
  separate(title_clean, c("Issue", "Funding"), sep = " \\| ") %>% 
  mutate(Issue = factor(Issue, levels = c("Human rights", "Humanitarian assistance")),
         Funding = factor(Funding, levels = c("Government", "Private"))) %>% 
  arrange(Issue, Funding) %>% 
  mutate_at(vars(theta_1, theta_2, theta_diff, pct_change), 
            funs(percent_format(accuracy = 0.1)(.))) %>% 
  mutate(p.diff.not0 = as.character(round(p.diff.not0, 2))) %>%
  mutate(Frame = paste0(Issue, " issues, ", Funding, " funding")) %>% 
  select(`H~2a~ and H~3a~ (nested)` = Frame,
         `% likely~Crackdown~` = theta_2, `% likely~No\\ crackdown~` = theta_1,
         `∆` = theta_diff, `%∆` = pct_change, `p(∆ ≠ 0)` = p.diff.not0)
```

@@

tbl_amount_1 <- tbl_amounts_tidy %>% 
  left_join(tbl_amounts_probs, by = "title") %>% 
  filter(category == "Level 1") %>%
  mutate(title = recode(title, 
                        Crackdown = "Crackdown − No crackdown",
                        Issue = "*Humanitarian assistance − Human rights*",
                        Funding = "*Private − Government funding*")) %>% 
  mutate_at(vars(mu_1, mu_2, mu_diff, p.diff.not0), funs(as.character(round(., 2)))) %>% 
  mutate(pct_change = percent_format(accuracy = 0.1)(pct_change)) %>%
  select(`Frame` = title, `Amount~Treatment~` = mu_2, `Amount~Control~` = mu_1,
         `∆` = mu_diff, `%∆` = pct_change, `p(∆ ≠ 0)` = p.diff.not0)
```

```{r tbl-amount-diffs-level2, warning=FALSE, message=FALSE}
tbl_amount_2 <- tbl_amounts_tidy %>% 
  left_join(tbl_amounts_probs, by = "title") %>% 
  filter(category == "Level 2") %>%
  mutate(title_clean = str_remove(title, " \\| Crackdown")) %>% 
  mutate(title_clean = case_when(
    title_clean %in% c("Human rights", "Humanitarian assistance") ~ paste(title_clean, "issues"),
    title_clean %in% c("Government", "Private") ~ paste(title_clean, "funding")
  )) %>% 
  mutate(title_clean = factor(title_clean, 
                              levels = c("Human rights issues", 
                                         "Humanitarian assistance issues", 
                                         "Government funding", "Private funding"))) %>% 
  arrange(title_clean) %>% 
  mutate_at(vars(mu_1, mu_2, mu_diff, p.diff.not0), funs(as.character(round(., 2)))) %>% 
  mutate(pct_change = percent_format(accuracy = 0.1)(pct_change)) %>%
  mutate(title_clean = as.character(title_clean)) %>% 
  select(`H~2b~ and H~3b~` = title_clean, `Amount~Crackdown~` = mu_2, `Amount~No\\ crackdown~` = mu_1,
         `∆` = mu_diff, `%∆` = pct_change, `p(∆ ≠ 0)` = p.diff.not0)
```

```{r tbl-amount-diffs-level3, warning=FALSE, message=FALSE}
tbl_amount_3 <- tbl_amounts_tidy %>% 
  left_join(tbl_amounts_probs, by = "title") %>% 
  filter(category == "Level 3") %>%
  mutate(title_clean = str_remove(title, " \\| Crackdown")) %>% 
  separate(title_clean, c("Issue", "Funding"), sep = " \\| ") %>% 
  mutate(Issue = factor(Issue, levels = c("Human rights", "Humanitarian assistance")),
         Funding = factor(Funding, levels = c("Government", "Private"))) %>% 
  arrange(Issue, Funding) %>% 
  mutate(Frame = paste0(Issue, " issues, ", Funding, " funding")) %>% 
  mutate_at(vars(mu_1, mu_2, mu_diff, p.diff.not0), funs(as.character(round(., 2)))) %>% 
  mutate(pct_change = percent_format(accuracy = 0.1)(pct_change)) %>%
  select(`H~2b~ and H~3b~ (nested)` = Frame,
         `Amount~Crackdown~` = mu_2, `Amount~No\\ crackdown~` = mu_1,
         `∆` = mu_diff, `%∆` = pct_change, `p(∆ ≠ 0)` = p.diff.not0)
```

>>>>

tbl_likely_1 <- tbl_likely_tidy %>% 
  left_join(tbl_likely_probs, by = "title") %>% 
  filter(category == "Level 1") %>%
  mutate(title = recode(title, 
                        Crackdown = "Crackdown − No crackdown",
                        Issue = "*Humanitarian assistance − Human rights*",
                        Funding = "*Private − Government funding*")) %>% 
  mutate_at(vars(theta_1, theta_2, theta_diff, pct_change), 
            funs(percent_format(accuracy = 0.1)(.))) %>% 
  mutate(p.diff.not0 = as.character(round(p.diff.not0, 2))) %>%
  select(Frame = title, `% likely~Treatment~` = theta_2, `% likely~Control~` = theta_1,
         `$\\Delta$` = theta_diff, `$\\%\\Delta$` = pct_change, 
         `$p(\\Delta \\neq 0)$` = p.diff.not0)
```

```{r tbl-likely-diffs-level2, warning=FALSE, message=FALSE}
tbl_likely_2 <- tbl_likely_tidy %>% 
  left_join(tbl_likely_probs, by = "title") %>% 
  filter(category == "Level 2") %>%
  mutate(title_clean = str_remove(title, " \\| Crackdown")) %>% 
  mutate(title_clean = case_when(
    title_clean %in% c("Human rights", "Humanitarian assistance") ~ paste(title_clean, "issues"),
    title_clean %in% c("Government", "Private") ~ paste(title_clean, "funding")
  )) %>% 
  mutate(title_clean = factor(title_clean, 
                              levels = c("Human rights issues", 
                                         "Humanitarian assistance issues", 
                                         "Government funding", "Private funding"))) %>% 
  arrange(title_clean) %>% 
  mutate_at(vars(theta_1, theta_2, theta_diff, pct_change), 
            funs(percent_format(accuracy = 0.1)(.))) %>% 
  mutate(p.diff.not0 = as.character(round(p.diff.not0, 2))) %>% 
  mutate(title_clean = as.character(title_clean)) %>% 
  select(`H~2a~ and H~3a~` = title_clean, 
         `% likely~Crackdown~` = theta_2, `% likely~No\\ crackdown~` = theta_1,
         `$\\Delta$` = theta_diff, `$\\%\\Delta$` = pct_change, 
         `$p(\\Delta \\neq 0)$` = p.diff.not0)
```

```{r tbl-likely-diffs-level3, warning=FALSE, message=FALSE}
tbl_likely_3 <- tbl_likely_tidy %>% 
  left_join(tbl_likely_probs, by = "title") %>% 
  filter(category == "Level 3") %>%
  mutate(title_clean = str_remove(title, " \\| Crackdown")) %>% 
  separate(title_clean, c("Issue", "Funding"), sep = " \\| ") %>% 
  mutate(Issue = factor(Issue, levels = c("Human rights", "Humanitarian assistance")),
         Funding = factor(Funding, levels = c("Government", "Private"))) %>% 
  arrange(Issue, Funding) %>% 
  mutate_at(vars(theta_1, theta_2, theta_diff, pct_change), 
            funs(percent_format(accuracy = 0.1)(.))) %>% 
  mutate(p.diff.not0 = as.character(round(p.diff.not0, 2))) %>%
  mutate(Frame = paste0(Issue, " issues, ", Funding, " funding")) %>% 
  select(`H~2a~ and H~3a~ (nested)` = Frame,
         `% likely~Crackdown~` = theta_2, `% likely~No\\ crackdown~` = theta_1,
         `$\\Delta$` = theta_diff, `$\\%\\Delta$` = pct_change, 
         `$p(\\Delta \\neq 0)$` = p.diff.not0)
```

@@

tbl_amount_1 <- tbl_amounts_tidy %>% 
  left_join(tbl_amounts_probs, by = "title") %>% 
  filter(category == "Level 1") %>%
  mutate(title = recode(title, 
                        Crackdown = "Crackdown − No crackdown",
                        Issue = "*Humanitarian assistance − Human rights*",
                        Funding = "*Private − Government funding*")) %>% 
  mutate_at(vars(mu_1, mu_2, mu_diff, p.diff.not0), funs(as.character(round(., 2)))) %>% 
  mutate(pct_change = percent_format(accuracy = 0.1)(pct_change)) %>%
  select(`Frame` = title, `Amount~Treatment~` = mu_2, `Amount~Control~` = mu_1,
         `$\\Delta$` = mu_diff, `$\\%\\Delta$` = pct_change, 
         `$p(\\Delta \\neq 0)$` = p.diff.not0)
```

```{r tbl-amount-diffs-level2, warning=FALSE, message=FALSE}
tbl_amount_2 <- tbl_amounts_tidy %>% 
  left_join(tbl_amounts_probs, by = "title") %>% 
  filter(category == "Level 2") %>%
  mutate(title_clean = str_remove(title, " \\| Crackdown")) %>% 
  mutate(title_clean = case_when(
    title_clean %in% c("Human rights", "Humanitarian assistance") ~ paste(title_clean, "issues"),
    title_clean %in% c("Government", "Private") ~ paste(title_clean, "funding")
  )) %>% 
  mutate(title_clean = factor(title_clean, 
                              levels = c("Human rights issues", 
                                         "Humanitarian assistance issues", 
                                         "Government funding", "Private funding"))) %>% 
  arrange(title_clean) %>% 
  mutate_at(vars(mu_1, mu_2, mu_diff, p.diff.not0), funs(as.character(round(., 2)))) %>% 
  mutate(pct_change = percent_format(accuracy = 0.1)(pct_change)) %>%
  mutate(title_clean = as.character(title_clean)) %>% 
  select(`H~2b~ and H~3b~` = title_clean, `Amount~Crackdown~` = mu_2, `Amount~No\\ crackdown~` = mu_1,
         `$\\Delta$` = mu_diff, `$\\%\\Delta$` = pct_change, 
         `$p(\\Delta \\neq 0)$` = p.diff.not0)
```

```{r tbl-amount-diffs-level3, warning=FALSE, message=FALSE}
tbl_amount_3 <- tbl_amounts_tidy %>% 
  left_join(tbl_amounts_probs, by = "title") %>% 
  filter(category == "Level 3") %>%
  mutate(title_clean = str_remove(title, " \\| Crackdown")) %>% 
  separate(title_clean, c("Issue", "Funding"), sep = " \\| ") %>% 
  mutate(Issue = factor(Issue, levels = c("Human rights", "Humanitarian assistance")),
         Funding = factor(Funding, levels = c("Government", "Private"))) %>% 
  arrange(Issue, Funding) %>% 
  mutate(Frame = paste0(Issue, " issues, ", Funding, " funding")) %>% 
  mutate_at(vars(mu_1, mu_2, mu_diff, p.diff.not0), funs(as.character(round(., 2)))) %>% 
  mutate(pct_change = percent_format(accuracy = 0.1)(pct_change)) %>%
  select(`H~2b~ and H~3b~ (nested)` = Frame,
         `Amount~Crackdown~` = mu_2, `Amount~No\\ crackdown~` = mu_1,
         `$\\Delta$` = mu_diff, `$\\%\\Delta$` = pct_change, 
         `$p(\\Delta \\neq 0)$` = p.diff.not0)
```
